Lazy Linearity for a Core Functional Language

### 2025-10-18 popl26.tex
target

\ROUNDTWO{The reader may wonder whether the complexities of our
  system hinted above are a better alternative to simply specializing
  the optimisation passes to produce code that passes a more naive
  linearity check. This avenue was already explored during the
  implementation of Linear
  Haskell in
  GHC\footnote{https://gitlab.haskell.org/ghc/ghc/-/issues/22123},
 exhibiting the prohibitive cost of too often restricting
 optimisations and producing less efficient code. Our work adheres to
 the principle that the type system bends to the optimisations, not
 the other way around.}
\noindent \ROUNDTWO{While GHC's Core language is our main focus, we
note that the ideas explored in this work can potentially be applied to any
language with non-strict features, even if the language itself is strict.}

>>>>

\ROUNDTWO{The reader may wonder whether the complexities of our
  system hinted above are a better alternative to simply specializing
  the optimisation passes to produce code that passes a more naive
  linearity check. This avenue was already explored during the
  implementation of Linear
  Haskell in
  GHC\footnote{https://gitlab.haskell.org/ghc/ghc/-/issues/22123},
 exhibiting the prohibitive cost of too often restricting
 optimisations and producing less efficient code. Our work adheres to
 the principle that the type system bends to the optimisations, not
 the other way around.}

 \ROUNDTWO{While GHC's Core language is our main focus, we
note that the ideas explored in this work can potentially be applied to any
language with non-strict features, even if the language itself is
strict. We assume some familiarity with Haskell and linear types for
functional languages, but try to explain our work and motivations
without assuming much knowledge of GHC and Core. }
